\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-08-09 Manuscript/reply.tex
responded to some comments

\subsection*{To Associate Editor}

\begin{comment}
Using Devon Allen's disqualification at the 2022 World Track and Field
championships as a hook, this paper poses two questions. First, were reaction
times at the 2022 World Track and Field Championships faster than they had been
earlier in 2022 national-level competitions, the 2019 World Track and Field
Championships, and the 2023 World Track and Field Championships? Second, based
on modeled reaction times, is the current standard of a 0.1 second threshold for
reaction times before disqualification too conservative?
\end{comment}

Thank you very much for your encouraging comments and great suggestion.  
We have now included a new section, \textit{Section 5 Classroom Implementation},
that discusses how elements of this manuscript have been incorporated into both 
graduate- and undergraduate-level teaching at the authors' home university.

For blinding purposes, course numbers, author initials and websites, and 
university name have been redacted, but all this information appears in the 
unblinded version.  In brief, this material has been covered at the graduate
level in a statistical computing course, open to all graduate students in 
Statistics and others with permission, that covers the bootstrap. Detailed R 
code and graphical illustrations were provided to students in the open-access 
course notes to elucidate the distinctions between employing null
hypotheses with and without defined parameters.  This link is included in the 
unblinded version of the paper; for the blinded review, we printed the 
relevant portion of the notes to pdf and included this blinded pdf file in the 
Supplemental Materials. %\eds{Not sure how we can blind your github 
%website for the submission unless we actually don't include it in the blinded 
%version. Could we print to PDF the relevant section of the notes and include as 
%a supplement for review purposes?}

Similarly at the undergraduate-level, students in an R-based applied regression 
course were provided with an R Markdown file with simulation code in order to 
demonstrate how the KS test fails with estimated parameters in the hypothesized 
distribution. The R Markdown file that was provided to students is included in 
the Supplemental Materials. This R-based applied linear regression course 
has the following prerequisites: two semesters of introductory statistics OR a 
Calculus~2-based statistical methods course.

At both the graduate and undergraduate level, students were able to follow the 
demonstrations closely and gain a clear understanding of the implications of 
using estimated parameters within test statistics.  At the graduate level, 
students further were able to appreciate the efficacy of the parametric 
bootstrap method as a corrective measure.

@@

We have included other sprinting events in our analysis.

@@

Yes, the comments about the difficulty of data gathering are meant to demostrate
that we worked hard to find as much data as we could and as a note to World
Athletics (track and field governing body) that they need to do a better job
at data standardization.  Currently the races on their website do not include
reaction times, which meant that we had to look in alternative places to perform
the analysis that we did.

@@

>>>>

@@

We are attempting to answer question 1 and have included reaction times from
additional sprinting events from World Championships.  We hypothesized that
as the length of the race increased, reaction time would be less impactful and
thus not as important. We started by adding data for the 100 meter dash and that
is the most similar event in terms of length to the 110 meter hurdles.  When we
added an additional variable to the model based on whether the observation came
from a dash event or hurdles event the coefficient was not significant.  An 
ANOVA test likewise produced a not signficant coefficient indicating to us that
it seems reasonable to pool the 100 meter dash and 110 meter hurdles.  We
hypothesized that longer sprinting events (200 meter dash, 400 meter dash, 400
meter hurdles) would be more difficult to add as those are longer races where
athletes reactions times are not as important to their overall time in the race.
When we repeat the procedure we did for the 100 meter dash, now looking at data
that included the 100 meter dash, 110 meter hurdles, and the 200 meter dash we
found that the coefficient on event type was signficant, and a p value of 0.01586.
When we peformed a TukeyHSD test to compare the times in the three categories:
100 meter dash, 110 meter hurdles, 200 meter dash, we found a p-value of
0.0020625 comparing the means of the 200 meter dash and the 110 meter hurdles
and a p-value of 0.0000174 comparing the means of the 100 meter dash and the 200
meter dash.  This indicated to us that the reaction times for the 200 meter were
too slow to fit into our study on extreme reaction times and thus we chose to
exclude 200 meter data.

@@

Yes, the comments about the difficulty of data gathering are meant to demostrate
that we worked hard to find as much data as we could and as a note to World
Athletics (track and field governing body) that they need to do a better job
at data standardization.  Currently the races on their website do not include
reaction times, which meant that we had to look in alternative places to perform
the analysis that we did.  The data we found from national level meets in 2022
was difficult to come by as it required searching for every country's championship
results individually and when we did find it, it was often in the native language
making it harder to understand and interpret.

@@

\begin{comment}
We have taken additional steps to streamline the manuscript and enhance the
presentation of our work. Thank you for your time and we appreciate re-considering
our submission.
\end{comment}
